My title

### 2024-09-14 outputs/paper/paper.qmd
finishes discussion

# Discussion

>>>>

# Discussion
Based on the analysis in the results section, we observe that although the overall population of homeless individuals in Toronto has not changed significantly over the past six years, its demographics have shifted considerably. Specifically, the proportions of refugees, chronically homeless individuals, and working-aged people have increased. In the past, the City of Toronto focused its efforts on reducing homelessness, primarily through projects aimed at building affordable housing @torontosol. However, our study indicates that with these demographic changes, the city government must also adopt additional strategies to address homelessness effectively.

First, as highlighted in the results section, the proportion of chronically homeless individuals has nearly doubled in the past six years. While chronic homelessness inherently involves long-lasting periods without stable housing, studies have shown that it is closely associated with chronic illness and mental health issues @chronic. Research further reveals that individuals experiencing mental illness or other disorders tend to have significantly lower incomes than the general population @Sareen2011. Consequently, those already facing mental and physical health challenges find it exceptionally difficult to escape homelessness. Additionally, homeless individuals often encounter more severe health problems due to inadequate nutrition, discrimination, and barriers to healthcare @Sleet2021. These factors create a vicious cycle: illness leads to decreased income, which leads to homelessness, which in turn worsens the illness.

To break this cycle, the city government should strengthen public healthcare systems, particularly for low-income and homeless populations. Building affordable housing alone has, in some cases, led to an increase in the proportion of chronically homeless individuals @house_not. Instead, the city should invest in supportive housing, where healthcare, mental health services, and social support are integrated with affordable housing. Given the strong link between chronic homelessness and mental health challenges, the city should also expand access to mental health and addiction services. Mobile outreach teams and community-based mental health clinics can help ensure that homeless individuals receive the care they need. Programs that reduce healthcare barriers—such as mobile health clinics, telehealth services, and partnerships with local hospitals—will improve health outcomes for homeless individuals and prevent them from becoming chronically homeless.

Second, due to increased global conflicts in Eastern Europe and the Middle East, the number of refugees entering Toronto has risen significantly @cbc23. However, the city has been unprepared to support this influx, as the proportion of refugees among the homeless population has surged from less than 20% in the first three quarters of 2021 to nearly 60% by the second quarter of 2024. There is an urgent need for the government to accelerate its efforts in assisting newly arrived refugees, providing them with jobs and secure housing.

Finally, we observe an increase in the proportion of working-aged homeless individuals. This underscores the need for the government to create more job opportunities, particularly for those who rely on employment to make a living, such as individuals experiencing mental health challenges or physical disabilities.
